Synthesizing Symmetric Lenses

### 2018-07-10 papers/SymmetricLenses/main.tex
fill in citations

In our setting, we already have a way of expressing sets of data:
regular expressions.  What we need is a way to express probability
distributions over that data.
To that end, we adopt \emph{stochastic regular expressions}~\cite{?} (SREs), 
which are regular expressions where each operator is annotated with a
probability.  A stochastic regular expression
specifies both a set of strings and a probability
distribution over it.  From this information, we can calculate the
entropy of the SRE.

@@

\subsection{Stochastic Regular Expression Equivalences}
$\Expand$ needs to be able to find equivalent stochastic regular expressions.
However, existing work does not provide a means to reason about stochastic
regular expression equivalence. We extend the \emph{star-semiring}~\cite{?}
equivalences to stochastic regular expressions.

@@

The \MergeR lens is interesting because it merges data where one data can be in
two formats, and one data has only one format. In previous work~\cite{?}, this
was combined into \OrLens{}, where \OrLens{} could have ambiguous types, but we
find it more clear to have explicit merge operators: it is easier to see what
lens the synthesis algorithm is creating.

>>>>

In our setting, we already have a way of expressing sets of data:
regular expressions.  What we need is a way to express probability
distributions over that data.
To that end, we adopt \emph{stochastic regular expressions}~\cite{stoch-def,stoch-rnn} (SREs), 
which are regular expressions where each operator is annotated with a
probability.  A stochastic regular expression
specifies both a set of strings and a probability
distribution over it.  From this information, we can calculate the
entropy of the SRE.

@@

\subsection{Stochastic Regular Expression Equivalences}
$\Expand$ needs to be able to find equivalent stochastic regular expressions.
However, existing work does not provide a means to reason about stochastic
regular expression equivalence. We extend the \emph{star-semiring}~\cite{Droste2009}
equivalences to stochastic regular expressions.

@@

The \MergeR lens is interesting because it merges data where one data can be in
two formats, and one data has only one format. In previous
work~\cite{Boomerang}, this was combined into \OrLens{}, where
\OrLens{} could have ambiguous types, but we find it more clear to have explicit
merge operators: it is easier to see what lens the synthesis algorithm is
creating.
